TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-10 paper/draft.tex
gaia subsection placeholder note
add subsection headers
rewrite intro outline; rename section labels

In this work we build a data-driven model for M dwarf spectra with \thecannon\ \citep{Ness:2015,Casey:2016,Ho:2017a,Behmard2019}: a fully empirical model, which employs no use of line lists or radiative transfer models. 
\thecannon\ is instead a \emph{generative model} which parameterizes the flux at each pixel of a spectrum in terms of a set of stellar labels (a flexible number of parameters chosen by the user; described in more detail in Section \ref{sec:cannon}). The model in this sense is used to \emph{transfer} labels from spectra for which we know parameters to those which we do not. Hence this data-driven approach effectively circumvents the challenges of physically modeling the atmosphere of a star (and common issues associated such as incomplete line lists or opacities), provided that we have a subset of spectra in the dataset with known (and very accurately measured) \emph{reference labels} possibly measured from other data.

@@

This paper is organized as follows: in Section \ref{sec:data} we describe the technical specifications of the data from the APOGEE survey and previous studies of M dwarfs in APOGEE, as well as our sample selection and derivation of training parameters. 
Section \ref{sec:cannon} describes our model implementation using \thecannon\ framework.
In Section \ref{sec:results} we present our experimental results, evaluate the predictive accuracy of our models, apply our model to a selected test sample of $>$10,000 sources, and examine the validity of our parameters against color-temperature relations and isochrone grids.
Finally, in Section \ref{sec:discussion} we discuss model performance, future improvements, and implications of our results in the context of present and upcoming stellar and exoplanetary surveys.

@@

%%==========================================================================================
\section{Method}\label{sec:cannon}

@@

%%==========================================================================================
\section{Sample Selection}

@@

@@

>>>>

In this work we build a data-driven model for M dwarf spectra with \thecannon\ \citep{Ness:2015,Casey:2016,Ho:2017a,Behmard2019}: a fully empirical model, which employs no use of line lists or radiative transfer models. 
\thecannon\ is instead a \emph{generative model} which parameterizes the flux at each pixel of a spectrum in terms of a set of stellar labels (a flexible number of parameters chosen by the user; described in more detail in Section \ref{sec:methods}). The model in this sense is used to \emph{transfer} labels from spectra for which we know parameters to those which we do not. Hence this data-driven approach effectively circumvents the challenges of physically modeling the atmosphere of a star (and common issues associated such as incomplete line lists or opacities), provided that we have a subset of spectra in the dataset with known (and very accurately measured) \emph{reference labels} possibly measured from other data.

@@

This paper is organized as follows: in Section \ref{sec:data} we describe the technical specifications of the data from the \apogee\ and \gaia\ surveys, as well as previous studies of M dwarfs in \apogee.
Section \ref{sec:methods} describes our model implementation using \thecannon\ framework, and Section \ref{sec:sample_selection} describes the our sample selection and derivation of training parameters.
In Section \ref{sec:results} we present our experimental results, evaluate the predictive accuracy of our models, apply our model to a selected test sample of $>$10,000 sources, and examine the validity of our parameters against color-temperature relations and isochrone grids.
Finally, in Section \ref{sec:discussion} we discuss model performance, future improvements, and implications of our results in the context of present and upcoming stellar and exoplanetary surveys.

@@

% ----------------------------------------
\subsection{\gaia\ Survey}

Need to talk about \gaia\ data \& what we use this dataset for...

%%==========================================================================================
\section{Method} \label{sec:methods}

@@

%%==========================================================================================
\section{Sample Selection} \label{sec:sample_selection}

@@

% ----------------------------------------
\subsection{Spectral Type Sample}

@@

% ----------------------------------------
\subsection{Physical Parameter Sample}
